
\begin{comment}
Our project set out to design, implement and fabricate an RF Oscillator, matching network and microstrip antenna on a PCB operating between 3.4 and 3.6GHz. We were centrally interested in understanding and implementing several of the main hardware building blocks found in communication systems.

\begin{enumerate}
\item Develop and validate a detailed Spice model for the selected transistor.
\item Design an oscillator circuit capable of generating the required frequency and analyze its stability, frequency accuracy, and harmonic content.
\item Design a matching network to achieve a \(50[\Omega]\) impedance match for the antenna and validate it through S-parameters analysis.
\item Develop and simulate the antenna system to be integrated into the transmitter, demonstrating efficiency and radiation patterns.
\item Fabricate the PCB according to the finalized layout, conduct comprehensive system testing, and validate performance metrics such as signal strength and reliability.
\end{enumerate}
\end{comment}

\begin{itemize}
    \item \textbf{Scientific Challenge}: Addressing the need for precise and stable oscillations at the 3.5 GHz frequency, crucial for modern wireless communication systems, including 5G networks and satellite communication.
    \item \textbf{Matching}: The design employs matching network to feed the load(Antenna) rather than a buffer, leading to space optimization.
    \item \textbf{Customization Requirement}: Overcoming the limitations of off-the-shelf oscillators that may not coincide with the characteristics of the antenna. Building both in parallel increases efficiency of design by ensuring the operating frequency stays in pass-band of antenna. 
    \item \textbf{System Reliability}: Designing a bespoke oscillator that ensures frequency stability, phase noise reduction, and power efficiency for a more reliable communication system.
    \item \textbf{Cost Efficiency}: Streamlining the design and manufacturing process to reduce production costs while maintaining high performance and reliability.
\end{itemize}